The College Application Problem

### 2022-05-06 slides_08min/slides.tex
typos; garbage collect unused latex imports

\newif\ifen\enfalse
% Language selector; must be on line 3
% Change to false to export Korean

\documentclass[11pt,slidestop,compress,mathserif,notheorems]{beamer}
\usetheme{CambridgeUS}
\setbeamercovered{transparent}
\usepackage[parfill]{parskip}
\usepackage{layout}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{relsize}
\usepackage{kotex}
\usepackage{diagbox}
\usepackage{multirow}
\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}
%\usepackage{bbold}
%\usepackage{kbordermatrix}
\usepackage{xcolor}
%\usepackage{cutwin}
\usepackage{tabularx}
%\usepackage{pgfplots}
%\usepgfplotslibrary{external} % Prevents memory overflow issues w pgfplots
%\tikzexternalize
%\setlength{\jot}{0pt}

@@

\begin{frame}%{Safety, target, and reach schools}
\vfill

@@

Solutions to the college application problem have \textbf{practical value}: US admissions consultants charge an average of \$200/hr (Sklarow 2018)!

@@

\begin{frame}{\ifen Appendix: Summary of algorithms\else 부록: 알고리즘 요약\fi}
\vfill\vspace{-1em}
\begin{center}
\ifen
\scalebox{0.90}{ 
\begin{tabular}{r|lllll}
\textbf{Algorithm} & \textbf{Problem} & \textbf{Restrictions} & \textbf{Exactness}       & \textbf{Computation time} \\ \hline
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Na\"ive\end{tabular} &  \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}     & None                  & $(1/h)$-opt.               & $O(m)$                    \\ 
\xrowht[()]{1.5em}  Greedy                &   \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}    & None                  & Exact                    & $O(hm)$                   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Branch and\\ bound\end{tabular}   & General          & None                  & Exact                    & $O(2^m)$                  \\
\xrowht[()]{1.5em}  Costs DP     &   General          & $g_j$ integer         & Exact                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.5em}  FPTAS      &   General          & None        & $(1 - \varepsilon)$-opt. & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Simulated\\annealing\end{tabular}   & General          & None                  & $0$-opt.                    & $O(Nm)$                
\end{tabular}
}
\else
\scalebox{1}{ 
\begin{tabular}{r|lllll}
\textbf{알고리즘} &  \textbf{문제} & \textbf{제한} & \textbf{정확도}       & \textbf{계산 시간} \\ \hline
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}나이브\end{tabular}                & \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}     & 없음                  & $(1/h)$-근사          & $O(m)$                    \\ 
\xrowht[()]{1.7em}  탐욕 해법               &  \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}    & 없음                  & 정확                    & $O(hm)$                   \\
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}분지한계법\end{tabular}   & 일반 문제          & 없음                  & 정확                    & $O(2^m)$                  \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}지출액\\ 동적 계획\end{tabular}    & 일반 문제          & $g_j$ 정수         & 정확                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.7em}  FPTAS       & 일반 문제          & 없음        & $(1 - \varepsilon)$-근사 & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}모의\\ 담금질\end{tabular}    & 일반 문제          & 없음                      & $0$-근사                    & $O(Nm)$                
\end{tabular}
}
\fi
\end{center}
\end{frame}

>>>>

\newif\ifen\entrue
% Language selector; must be on line 3
% Change to false to export Korean

\documentclass[11pt,mathserif,notheorems]{beamer}
\usetheme{CambridgeUS}
\usepackage[parfill]{parskip}
\usepackage{layout}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{relsize}
\usepackage{kotex}
\usepackage{diagbox}
\usepackage{multirow}
\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}
%\usepackage{bbold}
%\usepackage{kbordermatrix}
\usepackage{xcolor}
%\usepackage{cutwin}
\usepackage{tabularx}
%\usepackage{pgfplots}
%\usepgfplotslibrary{external} % Prevents memory overflow issues w pgfplots
%\tikzexternalize
%\setlength{\jot}{0pt}

@@

\begin{frame}%{Safety, target, and reach schools}

@@

\looseness=-1
Solutions to the college application problem have \textbf{practical value}: US admissions consultants charge an average of \$200/hr (Sklarow 2018)!

@@

\begin{frame}{\ifen Appendix: Summary of algorithms\else 부록: 알고리즘 요약\fi}
\begin{center}
\ifen
\scalebox{0.90}{ 
\begin{tabular}{r|lllll}
\textbf{Algorithm} & \textbf{Problem} & \textbf{Restrictions} & \textbf{Exactness}       & \textbf{Computation time} \\ \hline
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Na\"ive\end{tabular} &  \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}     & None                  & $(1/h)$-opt.               & $O(m)$                    \\ 
\xrowht[()]{1.5em}  Greedy                &   \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}    & None                  & Exact                    & $O(hm)$                   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Branch and\\ bound\end{tabular}   & General          & None                  & Exact                    & $O(2^m)$                  \\
\xrowht[()]{1.5em}  Costs DP     &   General          & $g_j$ integer         & Exact                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.5em}  FPTAS      &   General          & None        & $(1 - \varepsilon)$-opt. & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Simulated\\annealing\end{tabular}   & General          & None                  & $0$-opt.                    & $O(Nm)$                
\end{tabular}
}
\else
\scalebox{1}{ 
\begin{tabular}{r|lllll}
\textbf{알고리즘} &  \textbf{문제} & \textbf{제한} & \textbf{정확도}       & \textbf{계산 시간} \\ \hline
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}나이브\end{tabular}                & \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}     & 없음                  & $(1/h)$-근사          & $O(m)$                    \\ 
\xrowht[()]{1.7em}  탐욕 해법               &  \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}    & 없음                  & 정확                    & $O(hm)$                   \\
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}분지한계법\end{tabular}   & 일반 문제          & 없음                  & 정확                    & $O(2^m)$                  \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}지출액\\ 동적 계획\end{tabular}    & 일반 문제          & $g_j$ 정수         & 정확                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.7em}  FPTAS       & 일반 문제          & 없음        & $(1 - \varepsilon)$-근사 & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}모의\\ 담금질\end{tabular}    & 일반 문제          & 없음                      & $0$-근사                    & $O(Nm)$                
\end{tabular}
}
\fi
\end{center}
\end{frame}
